Dependent Object Types

### 2012-09-17 doc/fool/article.tex
typos
wrong info

Compared to Scala, DOT also simplifies type members. In DOT, a type
member is declared by its lower and upper bounds. Furthermore, unlike
Scala, there is no notion of uninstantiated type member. Here is an
example inspired by~\cite{vt}:
\begin{lstlisting}
trait Food
trait Animal {
  type Meal <: Food
  def eat(meal: Meal) {}
}
\end{lstlisting}
In Scala, \code{Meal} is an uninstantiated type member of \code{Animal}:
it is not possible to instantiate an \code{Animal} without providing a
concrete binding for \code{Meal}. In DOT, \code{Meal} is a type member
with a lower bound of $\Bot$ and an upper bound of \code{Food}. It is
possible to instantiate an \code{Animal} without further specifying
\code{Meal}, though it would not be possible to feed it. Now,
we define \code{Cow} by refining \code{Animal}.
\begin{lstlisting}
trait Grass extends Food
trait Cow extends Animal {
  type Meal = Grass
}
\end{lstlisting}
In Scala, the type alias \code{type Meal = Grass} defines a concrete
binding for \code{Meal}. Now, we can instantiate \code{Cow}s and feed
them \code{Grass}. In DOT, such a type alias is declared by giving it
identical lower and upper bounds.

DOT has a notion of concrete vs abstract type members, but it used to
distinguish which types members are instantiable as opposed to
instantiated. In the example above, all types introduced by
\code{trait} would be concrete type members in DOT with lower bounds
of $\Bot$ and upper bounds describing the \code{extends} clause:
$\Top$ for \code{Food}, a refinement of $\Top$ with type member
\code{Meal} and method member \code{eat} for \code{Animal},
\code{Food} for \code{Grass} and a refinement of \code{Animal} with
type member \code{Meal} for \code{Cow}. Concrete type members
typically have a lower bound of $\Bot$ so that they are purely
nominal: e.g. one needs to directly or indirectly instantiate a
\code{Cow} to have an object of type \code{Cow}.

@@

$a$ enforces that it's first argument be a $\mi{pets.Poodle_c}$ and it's second a $\mi{pets.Dalmatian_c}$. The following does not typecheck for this reason:
\begin{align*}
\cast \Top {\app {a.choose(d)} p}
\end{align*}

>>>>

Compared to Scala, DOT also simplifies type members. In DOT, a type
member is declared by its lower and upper bounds. Here is an example
inspired by~\cite{vt}:
\begin{lstlisting}
trait Food
trait Animal {
  type Meal <: Food
  def eat(meal: Meal) {}
}
\end{lstlisting}
\code{Meal} is a type member with a lower bound of $\Bot$ and an upper
bound of \code{Food}. It is possible to instantiate an \code{Animal}
without further specifying \code{Meal}, though it would not be
possible to feed it. Now, we define \code{Cow} by refining
\code{Animal}.
\begin{lstlisting}
trait Grass extends Food
trait Cow extends Animal {
  type Meal = Grass
}
\end{lstlisting}
In Scala, the type alias \code{type Meal = Grass} defines a concrete
binding for \code{Meal}. In DOT, such a type alias is declared by
giving it identical lower and upper bounds. Now, we can instantiate
\code{Cow}s and feed them \code{Grass}.

DOT has a notion of concrete vs abstract type members, which is used
to distinguish which types members are instantiable. In the example
above, all types introduced by \code{trait} would be concrete type
members in DOT with lower bounds of $\Bot$ and upper bounds describing
the \code{extends} clause: $\Top$ for \code{Food}, a refinement of
$\Top$ with type member \code{Meal} and method member \code{eat} for
\code{Animal}, \code{Food} for \code{Grass} and a refinement of
\code{Animal} with type member \code{Meal} for \code{Cow}. Concrete
type members typically have a lower bound of $\Bot$ so that they are
purely nominal: e.g. one needs to directly or indirectly instantiate a
\code{Cow} to have an object of type \code{Cow}.

@@

$a$ enforces that its first argument be a $\mi{pets.Poodle_c}$ and its second a $\mi{pets.Dalmatian_c}$. The following does not typecheck for this reason:
\begin{align*}
\cast \Top {\app {a.choose(d)} p}
\end{align*}
